FTLR proof cases

### 2018-03-07 fully-abstract-comp/ftlr-proof-cases.tex
Some work on FTLR proof.

\begin{lemma}
  If
  \begin{itemize}
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W_M}$
  \item $\npair{(b,e)}\in\readCond{l,W}$
  \item $a \in [b,e]$
  \item $W \oplus W_M$ is defined
  \item $n' < n$
  \end{itemize}
  Then $\npair[n']{(\ms_S(a),\ms_T(a))} \in \lrv(W')$ for some $W'$ such that $W_M = W' \oplus W_M'$.
  Additionally, if
  \begin{itemize}
  \item $\npair{(b,e)}\in\writeCond{l,W}$
  \end{itemize}
  Then $\memSat{(\ms_S[a\mapsto 0],\stk,\ms_\stk,\ms_T[a\mapsto 0])}{W_M'}$.
\end{lemma}
\begin{proof}
  From $\npair{(b,e)}\in\readCond{l,W}$, we get an $r \in \addressable{\lin,
    \pwheap}$ and $[\baddr',\eaddr'] \supseteq [\baddr,\eaddr]$ such that $\pwheap(r)
  \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}$.

@@

\section{FTLR proof}
By induction over $n$\footnote{if $n=0$, then we have a contradiction with $\Phi_S\term[i]$ and $\Phi_T\term[i]$ when we get to $\lro$.}.
\begin{proof}
  Assume
\[
  \npair{(b,e)}\in \readCond{\lin,W}
\]
and show
\[
\npair{((\rx,\lin),\baddr,\eaddr,\aaddr),
       ((\rx,\lin),\baddr,\eaddr,\aaddr)} \in \lre(W)
\]
We write $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$.\\

Let $n' \leq n$ be given and assume
\begin{enumerate}
\item $\npair[n']{[(c,c)]} \in \lrp(W)$ \dominique{Weird that this is an assumption here.  Shouldn't this be a proof obligation? Or rather: I think this should not be here at all but in the value relation instead? Remove this from the definition of $\lre$?}
\item $\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_R)$ \label{item:reg-ass}
\item $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$\label{item:mem-ass}
\item $W \oplus W_R \oplus W_M$ is well-defined.
\end{enumerate}
Further let
\begin{itemize}
\item $\Phi_S = (\ms_S,\reg_S\updReg{\pcreg}{c},\stk,\ms_\stk)$
\item $\Phi_T = (\ms_T,\reg_T\updReg{\pcreg}{c})$
\end{itemize}
and show
\[
  \npair[n']{(\Phi_S,\Phi_T)} \in \lro
\]
Let $i \leq n'$ be given \footnote{ignoring the frame...} and show
\[
  \Phi_S \term[i] \Rightarrow \Phi_T \term
\]
and 
\[
  \Phi_T \term[i] \Rightarrow \Phi_S \term
\]

\subsubsection*{Assuming source machine terminates}
First show the former of the two, assume $\Phi_S\term[i]$. We now consider the first step of $\Phi_S \term[i]$\footnote{if $i=0$, then we have a contradiction with $\Phi_S\term[i]$.}. 
The possible instructions that could have been executed are:
\begin{enumerate}
\item $\tfail$
\item $\thalt$
\item $\tjmp{\trg{r_1}}$
\item $\tjnz{\trg{r_1}}{\trg{\rn}}$
\item $\tisptr{\trg{r_1}}{\trg{r_2}}$
\item $\tgeta{\trg{r_1}}{\trg{r_2}}$
\item $\tgetb{\trg{r_1}}{\trg{r_2}}$
\item $\tgetp{\trg{r_1}}{\trg{r_2}}$
\item $\tgetlin{\trg{r_1}}{\trg{r_2}}$
\item $\tmove{\trg{r_1}}{\trg{\rn}}$
\item $\tstore{\trg{r_1}}{\trg{r_2}}$
\item $\tload{\trg{r_1}}{\trg{r_2}}$
\item $\tcca{\trg{r_1}}{\trg{\rn}}$
\item $\trestrict{\trg{r_1}}{\trg{r_2}}{\trg{\rn}}$
\item $\tlt{\trg{r_1}}{\trg{\rn}}{\trg{\rn}}$
\item $\tplus{\trg{r_1}}{\trg{\rn}}{\trg{\rn}}$
\item $\tminus{\trg{r_1}}{\trg{\rn}}{\trg{\rn}}$
\item $\tsetatob{\trg{r_1}}{\trg{r_2}}$
\item $\txjmp{\trg{r_1}}{\trg{r_1}}$
\item $\tcseal{\trg{r_1}}{\trg{r_2}}{\trg{r_3}}$
\item $\tsplice{\trg{r_1}}{\trg{r_2}}{\trg{r_3}}$
\item $\scall[o]{}{r_1}{r_2}$
\end{enumerate}

@@

\paragraph{Case: $\protect\thalt$}

>>>>

\begin{lemma}
  \label{lem:readcond-writecond-work}
  If
  \begin{itemize}
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W_M}$
  \item $\npair{(b,e)}\in\readCond{l,W}$
  \item $a \in [b,e]$
  \item $W \oplus W_M$ is defined
  \item $n' < n$
  \end{itemize}
  Then $\npair[n']{(\ms_S(a),\ms_T(a))} \in \lrv(W')$ for some $W'$ such that $W_M = W' \oplus W_M'$.
  Additionally, if
  \begin{itemize}
  \item $\npair{(b,e)}\in\writeCond{l,W}$
  \end{itemize}
  Then $\memSat{(\ms_S[a\mapsto 0],\stk,\ms_\stk,\ms_T[a\mapsto 0])}{W_M'}$.
\end{lemma}
\begin{proof}
  From $\npair{(b,e)}\in\readCond{l,W}$, we get an $r \in \addressable{\lin,
    \pwheap}$ and $[\baddr',\eaddr'] \supseteq [\baddr,\eaddr]$ such that $\pwheap(r)
  \nsubeq \stdreg{[\baddr',\eaddr']}{\pur}$.

@@

\section{FTLR proof}
By induction over $n$\footnote{if $n=0$, then we have a contradiction with $\Phi_S\term[i]$ and $\Phi_T\term[i]$ when we get to $\lro$.}.
\begin{proof}
  Assume
\[
  \npair{(\baddr,\eaddr)}\in \readCond{\lin,W}
\]
and show
\[
\npair{((\rx,\lin),\baddr,\eaddr,\aaddr),
       ((\rx,\lin),\baddr,\eaddr,\aaddr)} \in \lre(W)
\]
We write $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$.\\

Let $n' \leq n$ be given and assume
\begin{enumerate}
\item $\npair[n']{[(c,c)]} \in \lrp(W)$ \dominique{Weird that this is an assumption here.  Shouldn't this be a proof obligation? Or rather: I think this should not be here at all but in the value relation instead? Remove this from the definition of $\lre$?}
\item $\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_R)$ \label{item:reg-ass}
\item $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$\label{item:mem-ass}
\item $W \oplus W_R \oplus W_M$ is well-defined\label{item:worlds-def}
\end{enumerate}
Further let
\begin{itemize}
\item $\Phi_S = (\ms_S,\reg_S\updReg{\pcreg}{c},\stk,\ms_\stk)$
\item $\Phi_T = (\ms_T,\reg_T\updReg{\pcreg}{c})$
\end{itemize}
and show
\[
  \npair[n']{(\Phi_S,\Phi_T)} \in \lro
\]
Let $i \leq n'$ be given \footnote{ignoring the frame...} and show
\[
  \Phi_S \term[i] \Rightarrow \Phi_T \term
\]
and 
\[
  \Phi_T \term[i] \Rightarrow \Phi_S \term
\]

\subsubsection*{Assuming source machine terminates}
First show the former of the two, assume $\Phi_S\term[i]$.
Since $\Phi_S \neq \halted$, we have that $1 \leq i \leq n'$.

We know that $\Phi_S(\pcreg) = \Phi_T(\pcreg) = c$, $c=((\rx,\lin),\baddr,\eaddr,\aaddr)$ and $\npair{(\baddr,\eaddr)}\in \readCond{\lin,W}$.
From Lemma~\ref{lem:readcond-writecond-work}, using $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W_M}$ (from assumption~\ref{item:mem-ass}) and $W \oplus W_R \oplus W_M$ is well-defined (assumption~\ref{item:worlds-def}), we get (for any $a' \in [\baddr,\eaddr]$) that $\npair[n']{(\ms_S(a'),\ms_T(a'))} \in \lrv(W')$ for some $W'$ such that $W_M = W' \oplus W_M'$.

Since $\Phi_S \neq \halted$, this means that it must take a next execution step and also that $\Phi_S \not\step\failed$. 
This is only possible if one of the following holds:
\begin{itemize}
\item $\callCond{\Phi_S,r_1,r_2,\aaddr}$ and
  $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$ and 
  $\exec{\Phi_S(\pcreg)}$.

  In this case, we have for all $i = 0..\calllen-1$ that $\npair[n']{(\ms_S(\aaddr+i),\ms_T(\aaddr+i))} \in \lrv(W')$ for some $W'$, and also $\ms_S(\aaddr+i) \in \ints$, so by definition of $\lrv$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i)$.
\item ($\src{(\neg\callCond{\Phi_S,r_1,r_2,\aaddr}}$ or $\src{\eaddr < \aaddr + \calllen-1) \tand}$) and
  $\withinBounds{\Phi_S(\pcreg)}$ and $\exec{\Phi_S(\pcreg)}$.

  In this case, we have that $\npair[n']{(\ms_S(\aaddr),\ms_T(\aaddr))} \in \lrv(W')$ for some $W'$, and also $\ms_S(\aaddr) \in \ints$ (since $\Phi_S \not\step\failed$), so by definition of $\lrv$, we have that $\ms_T(\aaddr) = \ms_S(\aaddr)$.
\end{itemize}

We now consider the first step of $\Phi_S \term[i]$ (we have already mentioned that $i \geq 1$).
The possible instructions that could have been executed are:
\begin{enumerate}
\item $\tfail$
\item $\thalt$
\item $\tjmp{\trg{r_1}}$
\item $\tjnz{\trg{r_1}}{\trg{\rn}}$
\item $\tisptr{\trg{r_1}}{\trg{r_2}}$
\item $\tgeta{\trg{r_1}}{\trg{r_2}}$
\item $\tgetb{\trg{r_1}}{\trg{r_2}}$
\item $\tgetp{\trg{r_1}}{\trg{r_2}}$
\item $\tgetlin{\trg{r_1}}{\trg{r_2}}$
\item $\tmove{\trg{r_1}}{\trg{\rn}}$
\item $\tstore{\trg{r_1}}{\trg{r_2}}$
\item $\tload{\trg{r_1}}{\trg{r_2}}$
\item $\tcca{\trg{r_1}}{\trg{\rn}}$
\item $\trestrict{\trg{r_1}}{\trg{r_2}}{\trg{\rn}}$
\item $\tlt{\trg{r_1}}{\trg{\rn}}{\trg{\rn}}$
\item $\tplus{\trg{r_1}}{\trg{\rn}}{\trg{\rn}}$
\item $\tminus{\trg{r_1}}{\trg{\rn}}{\trg{\rn}}$
\item $\tsetatob{\trg{r_1}}{\trg{r_2}}$
\item $\txjmp{\trg{r_1}}{\trg{r_1}}$
\item $\tcseal{\trg{r_1}}{\trg{r_2}}{\trg{r_3}}$
\item $\tsplice{\trg{r_1}}{\trg{r_2}}{\trg{r_3}}$
\item $\scall[o]{}{r_1}{r_2}$
\end{enumerate}

@@

\paragraph{Case: $\protect\thalt$}
In this case $\Phi_S \step \halted$.
We've seen above that $\ms_T(\aaddr) = \ms_S(\aaddr)$, so because $\decInstr{}$ is shared by source and target, we have that $\Phi_T \step\halted$.
